---
title: "HydDB Annotation"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: sandstone
---

```{r, include=FALSE}
#save.image()
hyddbres.file <- snakemake@input[["hyddb"]]
cds.file <- snakemake@input[["cds"]]
commonscript.file <- snakemake@input[["commons"]]
threads <- snakemake@threads
bins <- data.frame(bin=snakemake@params$bins)
#taxcols=c("superkingdom","phylum","class","order","family","genus","species")
files <- unlist(c(hyddbres.file,cds.file))
source(commonscript.file)
suppressPackageStartupMessages(library(viridis))
commonOptions(threads)
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(scales))

hyddbres <- readData(hyddbres.file, bins)
setnames(hyddbres,c("query"),c("cds"),skip_absent = T)

cdsdat <- readData(cds.file,bins,readCDS)

hyddbres[grepl("\\[.+\\].+",Classification),Classification_Center:=sub("\\[(.+)\\].+","\\1",Classification)]
hyddbres[Classification=="NONHYDROGENASE",Classification_Center:="Rejected"]
hyddbres <- hyddbres[cdsdat,on="cds"]
```

# Overview

## Row

### Application Note

Kofam notes here

> Rendered at: `r Sys.time()`.

## Row

### File Note

```{r}
knitr::kable(genInfoBlock(files))
```
> The table shows the files which have been used to generate this report.


## Row

### CDS annotated

```{r}
hyddbrescounts = hyddbres[,.(N=length(unique(cds))),by=c("bin","Classification_Center")]
hyddbrescounts[,rel:=N/sum(N)*100,by="bin"]
hyddbrescounts = hyddbrescounts[!is.na(Classification_Center)]

ggplotly(ggplot(hyddbrescounts) + aes(x=bin,y=rel,fill=Classification_Center) + geom_bar(stat="identity",position="stack") + labs(x="Bin",fill="Classification",y="Of all CDS") + scale_y_continuous(labels = function(x) paste0(x, "%")))
```

> Which percentage of the CDS were annotated.  Rejected entries contained a RPS hit, but HydDB didn't classify them.

### Contigs annotated

```{r}
contigcounts = unique(hyddbres[,.(bin,cid,cds,subject)])
contigcounts = contigcounts[,.(rel=sum(!is.na(subject))/.N*100),by=c("bin","cid")]
ggplotly(ggplot(contigcounts) + aes(x=rel,color=bin) +  geom_freqpoly(aes(y=1*..density..*100),position='identity',binwidth=1) + labs(x="Of CDS in contig annotated",fill="Bin",y="Of all Contigs") + scale_x_continuous(labels = function(x) paste0(x, "%")) + scale_y_continuous(labels = function(x) paste0(x, "%")))
```

> Which percentage of the contigs contains a annotation?

## Row

### Score Distribution

```{r}
ggplotly(ggplot(hyddbres[!is.na(score)&score!=".",.(score=log10(as.numeric(eval)+1),bin)]) + aes(x=score, color=bin) + geom_density(trim=T) + labs(x="log10(eval+1)",y="Density estimate",color="Bin"))
```

> The distribution of the log10(e-values+1).

## Row 

### Model Hits

```{r,results="asis"}
hyddbrescounts = hyddbres[!is.na(subject),.(.N),by=c("bin","center","shortname","Classification_Center")]
hyddbrescounts[,rel:=N/sum(N)*100,by="bin"]
hyddbrescounts[,shortname:=paste0(center,":",shortname)]
hyddbrescounts=split(hyddbrescounts,hyddbrescounts$Classification_Center)

plots=lapply(hyddbrescounts,function(x)ggplotly(ggplot(x) + aes(x=bin,y=rel,fill=shortname) + geom_bar(stat="identity",position="stack") + labs(x="Bin",fill="Model",y="Of all Hits") + scale_y_continuous(labels = function(x) paste0(x, "%"))))
for(pname in names(plots)){
  drawplotasis(pname,"The Classification by HydDB and the models that identified that protein.",plots[[pname]])
}
```

## Row

### Bin Comparison

```{r}
dat=hyddbres[!is.na(Classification),.N,by=c("bin","Classification")]
dat[,rel:=N/sum(N)*100,by=c("bin")]
dat=as.data.table(complete(dat,bin,Classification,fill=list(N=0,rel=0)))
orderHeatMap(dat,"bin",field = "rel",grouping = "Classification")
orderHeatMap(dat,"Classification",field = "rel",grouping = "bin")
ggplotly(ggplot(dat)+aes_string(x="bin",y="Classification",fill="rel") +labs(fill="% of Hits")+ geom_raster() + xlab("Bin") + ylab("Predicted")+theme(axis.text.x = element_text(angle = 33)))
```

> The distribution of the HydDB hydrogenase classes.


